\documentclass{jthesis}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{setspace}
\usepackage{footmisc}
\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{listings}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
 
\lstdefinestyle{mystyle}{
    emph={self, Equation, loop, BlackHole2D,__init__, initialize, BlackHole, Application, Group},
    emphstyle=\color{PineGreen},
    commentstyle=\color{blue},
    keywordstyle={\color{BrickRed}\bfseries},
    numberstyle=\color{codegray},
    stringstyle=\color{codepurple},
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\title{The Effects of a Primordial Black Hole on the Surface of a Neutron Star} %Don't put a line break in, it gets really upset
\author{Brady Metherall}
\date{March 31, 2017}

\setlength\parindent{0pt}

\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Heavi}{H}

\DeclareMathOperator{\Hsign}{\mathscr{H}}
\newcommand\Hank[2][]{{\left( \Hsign_{#1} #2 \right) }}

\DeclareMathOperator{\grad}{\overset{\rightharpoonup}\nabla}

\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand\floatpagefraction{0.1}

\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}

\begin{document}

\pagenumbering{roman}
\maketitle

\makeabstract{
The identity of dark matter has piqued the interest of astrophysicists for quite some time. One of the possible candidates is primordial black holes, black holes possibly created by perturbations in the very early universe. Observations can put estimates on the mass ranges and number of primordial black holes in the universe which can determine their contribution to dark matter, as well as the conditions in the very early universe. In this thesis the effects a primordial black hole has on the surface of a neutron star if they were to collide is investigated. Neutron stars are treated as a flat infinite incompressible fluid in this toy model. The shape of the surface waves created, and the energy deposited into the neutron star, are found both analytically and with simulations.
}

\makeacknowledgements{
First and most importantly, I would like to thank my supervisor and mentor Dr. Joseph MacMillan for his assistance, guidance, and inspiration over the past four years, and especially the last eight months. \\

Next, I would like to express my gratitude to Dr. Sean Bohun, Dr. Mihai Beligan, and Dr. Mehran Ebrahimi for assisting me with solving difficult differential equations and mathematical proofs. As well as Dr. Hendrick de Haan for allowing me use of Polar for conducting my simulations. I would also like to thank my fellow physics students for helping make the last four years enjoyable. \\

Lastly, I would like to thank my mom and dad, and grandparents for their endless support and encouragement over the past four years.
}

\makedeclaration

\maketableofcontents

\pagenumbering{arabic}

\doublespacing
\linespread{2}
\lstset{style=mystyle}

\input{./1Introduction/Introduction}

\input{./2Transforms/Transforms}

\input{./3Analytic/Analytic}

\input{./4Simulation/Simulation}

\input{./5Conclusion/Conclusion}


\begin{thebibliography}{99}

\bibitem{fluids}
D. J. Acheson, \emph{Elementary Fluid Dynamics}, Oxford University Press, 1990.

\bibitem{massrange}
A. Barrau, D. Blais, G. Boudoul, D. Polarski, \emph{Peculiar Relics from Primordial Black Holes in the Inflationary Paradigm}, Annalen der Physik 13, 2003.

\bibitem{dynamicalfriction}
Fabio Capela, Maxim Pshirkov, and Peter Tinyakov, \emph{Constraints on Primordial Black Holes as Dark Matter Candidates from Capture by Neutron Stars}, American Physics Society Phys. Rev. D 87, 2013.

\bibitem{bigpaper}
Bernard Carr, Florian K{\"u}hnel, and Marit Sandstad, \emph{Primordial Black Holes as Dark Matter}, American Physical Society Phys. Rev. D 94, 2016.

\bibitem{massheavy}
B. J. Carr, and M. Sakellariadou, \emph{Dynamical Constraints on Dark Matter in Compact Objects}, The Astrophysical Journal 516, 1999.

\bibitem{cousin}
Pierre Cousin, \emph{Sur les Fonctions de $n$ Variables Complexes}, Acta Math. 19, 1895.

\bibitem{critdens}
Richard H. Cyburt, Brian D. Fields, Keith A. Olive, \emph{Primordial Nucleosynthesis in Light of WMAP}, Harvard Colloquia, 2003.

\bibitem{transforms}
Lokenath Debnath, and Dambaru Bhatta, \emph{Integral Transforms and Their Applications}, Chapman \& Hall/CRC, 2007.

\bibitem{tidalcapture}
Guillaume Defillon, Etienne Granet, Peter Tinyakov, and Michel H.G. Tytgat, \emph{On Tidal Capture of Primordial Black Holes by Neutron Stars}, American Physics Society Phys. Rev. D 90, 2014.

\bibitem{nuts}
Zachariah B. Etienne, Vasileios Paschalidis, Roland Hass, Philipp Moesta, Stuart L. Shapiro, \emph{IllinoisGRMHD: An Open-Source, User-Friendly GRMHD Code for Dynamical Spacetimes}, Classical and Quantum Gravity 32, 2015.

\bibitem{pessimism}
Paul H. Frampton, \emph{Searching for Dark Matter Constituents with Many Solar Masses}, World Scientific, 2016.

\bibitem{origsph}
R. A. Gingold, and J. J. Monaghan, \emph{Smoothed Particle Hydrodynamics: Theory and Application to Non-Spherical Stars}, Monthly Notices of the Royal Astronomical Society 181, 1977.

\bibitem{tableofints}
I. S. Gradshteyn, and I. M. Ryzhik, \emph{Table of Integrals, Series, and Products}, Elsevier Inc., 2007.

\bibitem{functional}
D. H. Griffel, \emph{Applied Functional Analysis}, Dover Publishing Inc., 2002.

\bibitem{hawking}
S. W. Hawking, \emph{Black Hole Explosions?}, Nature, 1974.

\bibitem{supersym}
G. Jungman, M. Kamionkowski, K. Griest, \emph{Supersymmetric Dark Matter}, Physics Report 267, 1996.

\bibitem{newsph}
J. J. Monaghan, \emph{Smoothed Particle Hydrodynamics}, Reports on Progress in Physics 68, 2005.

\bibitem{massfemt}
Robert J. Nemiroff, Gabriela F. Marani, Jay P. Norris, Jerry T. Bonnell, \emph{Limits on the Cosmological Abundance of Supermassive Compact Objects from a Millilensing Search in Gamma-Ray Burst Data}, Physical Review Letters 86, 2001.

\bibitem{a}
Paolo Pani, and Abraham Loeb, \emph{Tidal Capture of a Primordial Black Hole by a Neutron Star: Implications for Constrains on Dark Matter}, Journal of Cosmology and Astroparticle Physics, 2014.

\bibitem{pysph}
Prabhu Ramachandran, \emph{PySPH: a reproducible and high-performance framework for smoothed particle hydrodynamics}, In Proceedings of the 15th Python in Science Conference, 2016.

\bibitem{cosmology}
Barbara Ryden, \emph{Introduction to Cosmology}, Addison Wesley, 2003.

\bibitem{neutronmr}
Andrew W. Steiner, James M. Lattimer, and Edward F. Brown, \emph{The Neutron Star Mass-Radius Relation and the Equation of State of Dense Matter}, The Astrophysical Journal Letters 765, 2013.

\bibitem{mass1}
P. Tisserand, et al., \emph{Limits on the Macho Content of the Galactic Halo from the EROS-2 Survey of the Magellanic Clouds}, Astronomy \& Astrophysics, 2007.

\bibitem{massmilli}
P. N. Wilkinson, et al., \emph{Limits on the Cosmological Abundance of Supermassive Compact Objects form a Search for Multiple Imaging in Compact Radio Sources}, Physical Review Letters 86, 2001.


\end{thebibliography}

%\appendix
%
%\chapter{A Sample Appendix}
%\label{app:sample}
%
%This is just an example of an appendix.

\end{document}