\begin{thebibliography}{99}

\bibitem{fluids}
D. J. Acheson, \emph{Elementary Fluid Dynamics}, Oxford University Press, 1990.

\bibitem{massrange}
A. Barrau, D. Blais, G. Boudoul, D. Polarski, \emph{Peculiar Relics from Primordial Black Holes in the Inflationary Paradigm}, Annalen der Physik 13, 2003.

\bibitem{dynamicalfriction}
Fabio Capela, Maxim Pshirkov, and Peter Tinyakov, \emph{Constraints on Primordial Black Holes as Dark Matter Candidates from Capture by Neutron Stars}, American Physics Society Phys. Rev. D 87, 2013.

\bibitem{massheavy}
B. J. Carr, and M. Sakellariadou, \emph{Dynamical Constraints on Dark Matter in Compact Objects}, The Astrophysical Journal 516, 1999.

\bibitem{bigpaper}
Bernard Carr, Florian K{\"u}hnel, and Marit Sandstad, \emph{Primordial Black Holes as Dark Matter}, American Physical Society Phys. Rev. D 94, 2016.

\bibitem{cousin}
Pierre Cousin, \emph{Sur les Fonctions de $n$ Variables Complexes}, Acta Math. 19, 1895.

\bibitem{critdens}
Richard H. Cyburt, Brian D. Fields, Keith A. Olive, \emph{Primordial Nucleosynthesis in Light of WMAP}, Harvard Colloquia, 2003.

\bibitem{transforms}
Lokenath Debnath, and Dambaru Bhatta, \emph{Integral Transforms and Their Applications}, Chapman \& Hall/CRC, 2007.

\bibitem{tidalcapture}
Guillaume Defillon, Etienne Granet, Peter Tinyakov, and Michel H.G. Tytgat, \emph{On Tidal Capture of Primordial Black Holes by Neutron Stars}, American Physics Society Phys. Rev. D 90, 2014.

\bibitem{merger}
Zachariah B. Etienne, Joshua A. Faber, Yuk Tung Liu, Stuart L. Shapiro, Keisuke Taniguchi, and Thomas W. Baumgarte, \emph{Fully General Relativistic Simulations of Black Hole-Neutron Star Mergers}, American Physical Society Phys. Rev. D 77, 2008.

\bibitem{nuts}
Zachariah B. Etienne, Vasileios Paschalidis, Roland Hass, Philipp Moesta, Stuart L. Shapiro, \emph{IllinoisGRMHD: An Open-Source, User-Friendly GRMHD Code for Dynamical Spacetimes}, Classical and Quantum Gravity 32, 2015.

\bibitem{pessimism}
Paul H. Frampton, \emph{Searching for Dark Matter Constituents with Many Solar Masses}, World Scientific, 2016.

\bibitem{origsph}
R. A. Gingold, and J. J. Monaghan, \emph{Smoothed Particle Hydrodynamics: Theory and Application to Non-Spherical Stars}, Monthly Notices of the Royal Astronomical Society 181, 1977.

\bibitem{tableofints}
I. S. Gradshteyn, and I. M. Ryzhik, \emph{Table of Integrals, Series, and Products}, Elsevier Inc., 2007.

\bibitem{functional}
D. H. Griffel, \emph{Applied Functional Analysis}, Dover Publishing Inc., 2002.

\bibitem{hawking}
S. W. Hawking, \emph{Black Hole Explosions?}, Nature, 1974.

\bibitem{supersym}
G. Jungman, M. Kamionkowski, K. Griest, \emph{Supersymmetric Dark Matter}, Physics Report 267, 1996.

\bibitem{newsph}
J. J. Monaghan, \emph{Smoothed Particle Hydrodynamics}, Reports on Progress in Physics 68, 2005.

\bibitem{massfemt}
Robert J. Nemiroff, Gabriela F. Marani, Jay P. Norris, Jerry T. Bonnell, \emph{Limits on the Cosmological Abundance of Supermassive Compact Objects from a Millilensing Search in Gamma-Ray Burst Data}, Physical Review Letters 86, 2001.

\bibitem{a}
Paolo Pani, and Abraham Loeb, \emph{Tidal Capture of a Primordial Black Hole by a Neutron Star: Implications for Constrains on Dark Matter}, Journal of Cosmology and Astroparticle Physics, 2014.

\bibitem{mergerjets}
Vasileios Paschalidis, Milton Ruiz, and Stuart L. Shapiro, \emph{Relativistic Simulations of Black Hole-Neutron Star Coalescence: The Jet Emerges}, The Astrophysical Journal Letters 806, 2015.

\bibitem{pysph}
Prabhu Ramachandran, \emph{PySPH: a reproducible and high-performance framework for smoothed particle hydrodynamics}, In Proceedings of the 15th Python in Science Conference, 2016.

\bibitem{cosmology}
Barbara Ryden, \emph{Introduction to Cosmology}, Addison Wesley, 2003.

\bibitem{neutronmr}
Andrew W. Steiner, James M. Lattimer, and Edward F. Brown, \emph{The Neutron Star Mass-Radius Relation and the Equation of State of Dense Matter}, The Astrophysical Journal Letters 765, 2013.

\bibitem{mass1}
P. Tisserand, et al., \emph{Limits on the Macho Content of the Galactic Halo from the EROS-2 Survey of the Magellanic Clouds}, Astronomy \& Astrophysics, 2007.

\bibitem{massmilli}
P. N. Wilkinson, et al., \emph{Limits on the Cosmological Abundance of Supermassive Compact Objects from a Search for Multiple Imaging in Compact Radio Sources}, Physical Review Letters 86, 2001.

\end{thebibliography}